Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Caption for BQ regression figure

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{\textbf{Nonparametric model.} \TODO{}}
  \label{fig:bq}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{\textbf{Nonparametric model.} Each panel shows one step of
    the Bayesian Quadrature regression. Upper left: the original
    Gaussian Process (GP) regression for $S$. Lower left: the GP
    regression for $\log(S+1)$. Lower right: the GP regression for
    $\Delta_c=\mu_{\log S} - \log \mu_S$. Upper right: the adjusted
    regression for $S$, where the mean is equal to
    $\mu_S(1+\mu_{\Delta_c})$. The model uses this final estimate to
    compute $Z$ and will continue rotating until the variance of $Z$
    is low enough that a hypothesis may be accepted. This method
    allows the model to avoid local maxima such as the one near
    $\frac{\pi}{6}$, which causes trouble for the na\"ive and
    parametric models in Figure \ref{fig:simple-models}.}
  \label{fig:bq}
\end{figure}
